Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-22 index.Rmd
Grammar and spelling edits, Markdown styling
Also removes one "Other research question" that's not important to this work

This compendium details the statistical analysis and methods while undertaking a meta-analysis of fungicide efficacy trials for control of powdery mildew in mungbean. 
This meta-analysis will focus on the main aim of determining:

@@

## Contents
This compendia is broken down into seven sections:

   1. [Details of the experiments which were included in the analysis][Studies considered in meta-analysis].  
   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis.][Preliminary Analysis]  
      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray scheduale on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray scheduale on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]

## Other research questions which are not the focus of this study
+ How has the first sign of powdery mildew changed over the seasons and between
experimental sites?

@@

+ What is the length of a mungbean season and how has it varied in this trial?

   - This data has not been collected or is not accurate enough to be useful to
   answer this question.

@@

+ Variability among host genotypes.  
   + The probable influence of season might be influenced by host genotype. This
   is because newer varieties were adopted into experimental trials as they were
   released.

>>>>

This research compendium details the statistical analysis and methods of a meta-analysis of fungicide efficacy trials for controlling powdery mildew in mungbean.
The meta-analysis's main aim is to determine:

@@

## Contents
This compendium is broken down into seven sections:

   1. [Details of the experiments, which were included in the analysis][Studies considered in meta-analysis]  
   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]

## Other research questions, which are not the focus of this study

+ How has the first sign of powdery mildew changed between the seasons and experimental sites?

@@

@@

+ Variability among host genotypes.

   + The probable influence of season might be influenced by host genotype.
   This is because newer varieties were adopted into experimental trials as they were released.
